Lifting CDCL to Relational Domains

### 2016-10-13 experiments.tex
experiment description

\section{Experimental Results}\label{experiments}

>>>>

\section{Experimental Results}
We have implemented the instantiation of ACDCL on relational domains 
inside 2LS verification tool~\cite{}.  The abstract domains used for 
our experiments are intervals, template polyhedra, octagons and equalities.  
We verified a total of 70 benchmarks in ANSI-C, which are derived from 
(a) bit-vector regression category in SV-COMP'16, (c) bit-precise and 
cycle accurate software models of hardware circuits automatically 
generated using v2c~\cite{tacas16}, (c) controller code generated 
from Simulink (d) several hand-crafted benchmarks for equivalence 
checking and bounded loop analysis.  All the benchmarks containing 
bounded loops are completely unrolled before analysis.  We compare 
our tool with a state-of-the-art bounded model checker CBMC~\cite{cbmc} 
and a commercial abstract interpretation tool, Astr{\'e}e.  CBMC uses 
MiniSAT solver in the backend.  Astr\{'e}e was configured with interval 
domain, trace-partition domain, and relational domains.  To enable precise 
analysis using Astr{\'e}e, all our benchmarks are manually instrumented with 
partition directive which provides external hint to guide the trace partitioning 
heuristics inside the tool.  Usually, such high-precision makes the analysis
very expensive, and is not needed for static analysis of the code.  Without trace 
partitioning, the analysis using Astr{\'e}e shows high degree of imprecision.
